Supporting Information

### 2018-03-20 SupportingInformation.Rmd
changing table captions

```{r tab_count_LTdep_AICw, echo=F, results='markup'}
knitr::kable(RES_aphid_count$LTdep_AICw,
             format='pandoc',
             caption = "Aphid_count : model averaged lower tail dependence statistic for best fit copula family for each selective location pair\\label{tab_count_LTdep_AICw}",
             booktabs=TRUE
             )
```

```{r tab_count_UTdep_AICw, echo=F, results='markup'}
knitr::kable(RES_aphid_count$UTdep_AICw,
             format='pandoc',
             caption = "Aphid_count : model averaged upper tail dependence statistic for best fit copula family for each selective location pair\\label{tab_count_UTdep_AICw}",
             booktabs=TRUE
             )
```

```{r tab_count_LTmUT, echo=F, results='markup'}
knitr::kable(RES_aphid_count$LTdep_AICw-RES_aphid_count$UTdep_AICw,
             digits = 5,
             format='pandoc',
             caption = "Aphid_count : model averaged lower tail dependence statistic for best fit copula family for each selective location pair\\label{tab_count_LTmUT}",
             booktabs=TRUE
             )
```

@@

```{r tab_ff_LTdep_AICw, echo=F, results='markup'}
knitr::kable(RES_aphid_ff$LTdep_AICw,
             format='pandoc',
             caption = "Aphid_firstflight : model averaged lower tail dependence statistic for best fit copula family for each selective location pair\\label{tab_ff_LTdep_AICw}",
             booktabs=TRUE
             )
```

```{r tab_ff_UTdep_AICw, echo=F, results='markup'}
knitr::kable(RES_aphid_ff$UTdep_AICw,
             format='pandoc',
             caption = "Aphid_firstflight : model averaged upper tail dependence statistic for best fit copula family for each selective location pair\\label{tab_ff_UTdep_AICw}",
             booktabs=TRUE
             )
```

```{r tab_ff_LTmUT, echo=F, results='markup'}
knitr::kable(RES_aphid_ff$LTdep_AICw-RES_aphid_ff$UTdep_AICw,
             digits = 5,
             format='pandoc',
             caption = "Aphid_firstflight : model averaged lower tail dependence statistic for best fit copula family for each selective location pair\\label{tab_ff_LTmUT}",
             booktabs=TRUE
             )
```

@@

```{r tab_pns_LTdep_AICw,echo=F,results="markup"}
knitr::kable(RES_plankton_north_sea$LTdep_AICw,
             format="pandoc",
             digits=3,
             caption = "Plankton_north_sea : model averaged lower tail dependence statistic for best fit copula family for each selective location pair\\label{tab_pns_LTdep_AICw}",
             booktabs=TRUE)
```

```{r tab_pns_UTdep_AICw,echo=F,results="markup"}
knitr::kable(RES_plankton_north_sea$UTdep_AICw,
             format="pandoc",
             digits=3,
             caption = "Plankton_north_sea : model averaged upper tail dependence statistic for best fit copula family for each selective location pair\\label{tab_pns_UTdep_AICw}",
             booktabs=TRUE)
```

```{r tab_pns_LTmUT,echo=F,results="markup"}
knitr::kable(RES_plankton_north_sea$LTdep_AICw-RES_plankton_north_sea$UTdep_AICw,
             format="pandoc",
             digits=3,
             caption = "Plankton_north_sea : model averaged lower tail - model averaged upper tail dependence statistic for best fit copula family for each of the selective location pair\\label{tab_pns_LTmUT}",
             booktabs=TRUE)
```

>>>>

```{r tab_count_LTdep_AICw, echo=F, results='markup'}
knitr::kable(RES_aphid_count$LTdep_AICw,
             format='pandoc',
             caption = "Aphid_count : model averaged lower tail dependence statistic for each selective location pair\\label{tab_count_LTdep_AICw}",
             booktabs=TRUE
             )
```

```{r tab_count_UTdep_AICw, echo=F, results='markup'}
knitr::kable(RES_aphid_count$UTdep_AICw,
             format='pandoc',
             caption = "Aphid_count : model averaged upper tail dependence statistic for each selective location pair\\label{tab_count_UTdep_AICw}",
             booktabs=TRUE
             )
```

```{r tab_count_LTmUT, echo=F, results='markup'}
knitr::kable(RES_aphid_count$LTdep_AICw-RES_aphid_count$UTdep_AICw,
             digits = 5,
             format='pandoc',
             caption = "Aphid_count : model averaged lower tail dependence - model averaged upper tail dependence statistic for each selective location pair\\label{tab_count_LTmUT}",
             booktabs=TRUE
             )
```

@@

```{r tab_ff_LTdep_AICw, echo=F, results='markup'}
knitr::kable(RES_aphid_ff$LTdep_AICw,
             format='pandoc',
             caption = "Aphid_firstflight : model averaged lower tail dependence statistic for each selective location pair\\label{tab_ff_LTdep_AICw}",
             booktabs=TRUE
             )
```

```{r tab_ff_UTdep_AICw, echo=F, results='markup'}
knitr::kable(RES_aphid_ff$UTdep_AICw,
             format='pandoc',
             caption = "Aphid_firstflight : model averaged upper tail dependence statistic for each selective location pair\\label{tab_ff_UTdep_AICw}",
             booktabs=TRUE
             )
```

```{r tab_ff_LTmUT, echo=F, results='markup'}
knitr::kable(RES_aphid_ff$LTdep_AICw-RES_aphid_ff$UTdep_AICw,
             digits = 5,
             format='pandoc',
             caption = "Aphid_firstflight : model averaged lower tail dependence - model averaged upper tail dependence statistic for each selective location pair\\label{tab_ff_LTmUT}",
             booktabs=TRUE
             )
```

@@

```{r tab_pns_LTdep_AICw,echo=F,results="markup"}
knitr::kable(RES_plankton_north_sea$LTdep_AICw,
             format="pandoc",
             digits=3,
             caption = "Plankton_north_sea : model averaged lower tail dependence statistic for each selective location pair\\label{tab_pns_LTdep_AICw}",
             booktabs=TRUE)
```

```{r tab_pns_UTdep_AICw,echo=F,results="markup"}
knitr::kable(RES_plankton_north_sea$UTdep_AICw,
             format="pandoc",
             digits=3,
             caption = "Plankton_north_sea : model averaged upper tail dependence statistic for each selective location pair\\label{tab_pns_UTdep_AICw}",
             booktabs=TRUE)
```

```{r tab_pns_LTmUT,echo=F,results="markup"}
knitr::kable(RES_plankton_north_sea$LTdep_AICw-RES_plankton_north_sea$UTdep_AICw,
             format="pandoc",
             digits=3,
             caption = "Plankton_north_sea : model averaged lower tail - model averaged upper tail dependence statistic for each of the selective location pair\\label{tab_pns_LTmUT}",
             booktabs=TRUE)
```
